%-------------------------
% Resume in LaTeX
% Based on: github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  {\Large\textbf{Kelley Lynch}} \\[4pt]
  \small
  \href{mailto:kelleylynch@gmail.com}{kelleylynch@gmail.com} $|$
  (857) 999-5661 $|$
  \href{https://github.com/kelleyl}{github.com/kelleyl} $|$
  \href{https://kelleylynch.com}{kelleylynch.com}
\end{center}

%-----------SUMMARY----------
\section{Summary}
  \small{Computer Science PhD Candidate specializing in Computational Linguistics, Multimedia AI, and Vision-Language Models (VLMs). Expertise in agentic systems, prompt optimization, multimodal data annotation, and ontology development for information extraction in archival and industry contexts.}

%-----------SKILLS----------
\section{Skills}
  \begin{itemize}[leftmargin=*, label={}, itemsep=-2pt, parsep=2pt]
    \small{
      \item \textbf{AI/ML:} Vision-Language Models, Large Language Models, Agent Design \& Orchestration, Prompt Optimization (DSPy), Evaluation Frameworks, Data Annotation, NLP, Computer Vision
      \item \textbf{Tools:} Python, Go, PyTorch, OpenCV, Flask, Elasticsearch, Docker
      \item \textbf{Domains:} Multimedia Information Extraction, Ontology Development, Conversational AI, Synthetic Data Generation, MMIF
    }
  \end{itemize}

%-----------EXPERIENCE----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ph.D. Candidate, Computer Science}{Aug 2017 -- Present}
      {Brandeis University}{Waltham, MA}
      \resumeItemListStart
        \resumeItem{CLAMS Agent (Thesis)}{Designing an LLM/VLM-powered agentic system to orchestrate multimedia metadata extraction}
        \resumeItem{SDK \& Tools}{Integrating LLM interfaces into the CLAMS SDK; building apps like smolvlm2 for multimodal analysis}
        \resumeItem{Slates-500 Dataset}{Created a multimodal dataset and evaluation pipeline for information extraction from archival video slates}
        \resumeItem{Hawaii Chyron Dataset}{Curated a dataset for extracting Hawaiian language text from broadcast video using OCR and VLMs}
      \resumeItemListEnd

    \resumeSubheading
      {Research Scientist}{Sep 2022 -- Jan 2024}
      {Posh Inc.}{Boston, MA}
      \resumeItemListStart
        \resumeItemPlain{Led ontology development for enterprise conversational AI to improve intent recognition and dialogue flow}
        \resumeItemPlain{Analyzed customer interactions to identify edge cases, expand conversational models, and improve accuracy}
        \resumeItemPlain{Evaluated and optimized production AI models for scalable chatbot deployments}
      \resumeItemListEnd

    \resumeSubheading
      {ML Research Intern}{May 2022 -- Aug 2022}
      {Cobalt}{Boston, MA}
      \resumeItemListStart
        \resumeItemPlain{Evaluated GPT-3 for generating synthetic conversational data to train downstream models}
        \resumeItemPlain{Developed automated, NLP-driven summarization methods for customer support calls}
      \resumeItemListEnd

    \resumeSubheading
      {NLP Research Consultant}{May 2019 -- May 2021}
      {Booxby Inc.}{Sausalito, CA (Remote)}
      \resumeItemListStart
        \resumeItemPlain{Designed and tested end-to-end NLP pipelines for feature extraction and narrative analysis on large fiction collections}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS----------
\section{Selected Publications \& Presentations}

  \resumeSubHeadingListStart

    \resumeSubheadingSimple{CLAMS Platform}{\small Core developer and coauthor}
    \resumeItemListStart
      \resumeItemPlain{Rim, King, \textbf{Lynch}, Verhagen, Pustejovsky. \textit{A Platform for AI-Assisted Archival Metadata Generation.} HCI International, 2025.}
      \resumeItemPlain{\textbf{Lynch}, Rim, King, Pustejovsky. \textit{Multimodal Interoperability with the CLAMS Platform.} MMM 2025 (Demo).}
      \resumeItemPlain{Verhagen, \textbf{Lynch}, Rim, Pustejovsky. \textit{The CLAMS Platform at Work.} LREC 2022.}
      \resumeItemPlain{Rim, \textbf{Lynch}, Verhagen, Ide, Pustejovsky. \textit{Interchange Formats for Visualization: LIF and MMIF.} LREC 2020.}
      \resumeItemPlain{Rim, \textbf{Lynch}, Pustejovsky. \textit{Computational Linguistics Applications for Multimedia Services.} LaTeCH-CLfL 2019.}
      \resumeItemPlain{Workshop: \textit{Indexing the American Archive of Public Broadcasting.} Fantastic Futures 2019, Stanford.}
      \resumeItemPlain{Cariani, Pustejovsky, \textbf{Lynch}, Davis-Kaufman. \textit{Automated Creation of Descriptive Metadata for Large Media Archives.} JTS 2019, Amsterdam.}
    \resumeItemListEnd

    \resumeSubheadingSimple{Slates-500 Dataset}{}
    \resumeItemListStart
      \resumeItemPlain{Multimodal dataset and evaluation pipeline for information extraction from archival video slates. Under review.}
    \resumeItemListEnd

    \resumeSubheadingSimple{Hawaii Chyron Dataset}{}
    \resumeItemListStart
      \resumeItemPlain{Understanding On-Screen Text: Do AI Tools Struggle with Hawaiian Chyrons? IASA Journal (in review).}
      \resumeItemPlain{Presentations: IASA Conference, Honolulu (2025); Fantastic Futures Conference (2025).}
    \resumeItemListEnd

    \resumeSubheadingSimple{Video Content Summarization}{}
    \resumeItemListStart
      \resumeItemPlain{\textbf{Lynch}, Jiang, Lambright, Rim, Pustejovsky. \textit{Video Content Summarization with Large Language-Vision Models.} IEEE Big Data (CAS Workshop), 2024.}
      \resumeItemPlain{Presentation: Boston Digital Humanities Symposium, 2025.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingSimple{Ph.D., Computer Science -- Brandeis University}{Expected 2026}
    \resumeSubheadingSimple{M.A., Computational Linguistics -- Brandeis University}{2017}
    \resumeSubheadingSimple{B.S., Mathematics and French -- Centre College}{2013}
  \resumeSubHeadingListEnd

\end{document}
